List of Items

### 2021-03-16 index.Rmd
- update for NM&S submission

---
title: "Longitudinal Analysis of the Privacy Calculus"
---

On this website, you can find the companion material for the paper _A Longitudinal Analysis of the Privacy Paradox_.

@@

Please note that this OSM does not contain the actual data, which can be downloaded from http://dx.doi.org/10.7802/1937.

This website is produced directly from the project's [github repository](https://github.com/tdienlin/privacy_calc_exp). You can download the material, file an issue, or submit a pull request.

>>>>

---
title: "A longitudinal analysis of the privacy paradox"
---

On this website, you can find the companion material for the paper _A longitudinal analysis of the privacy paradox_.

@@

Please note that this OSM does not contain the actual data, which can be downloaded [here](http://dx.doi.org/10.7802/1937).

This website is produced directly from the project's [github repository](https://github.com/tdienlin/privacy-paradox-longitudinal). You can download the material, file an issue, or submit a pull request.

### 2021-03-16 items.Rmd
- update for NM&S submission

1. In general, how concerned are you about your privacy while using the Internet?
2. Are you concerned about online organizations not being who they claim they are?
3. Are you concerned about online identity theft?
4. Are you concerned about people you do not know obtaining personal information about you from your online activities?
5. Are you concerned that if you use your credit card to buy something on the Internet your credit card number will be obtained/intercepted by someone else?
6. Are you concerned that an email you sent may be read by someone else besides the person you sent it to?
7. Are you concerned that institutions or secret services could collect and analyze the data that you are disclosing on the Internet?
8. Are you concerned that website providers are tracking your online activities?
9. Are you concerned that you don’t know what other organizations or website providers are doing with you data?

@@

1. Financial information (bank data, account balances…)
2. Medical information (health, medical records…)
3. Second name
4. First name
5. Residence
6. Street and house number
7. Email address
8. Phone number
9. Photos (of you)
10. Job (past and present)
11. Education

>>>>

 - Are you concerned about people you do not know obtaining personal information about you from your online activities?
 - Are you concerned that if you use your credit card to buy something on the Internet your credit card number will be obtained/intercepted by someone else?
 - Are you concerned that an email you sent may be read by someone else besides the person you sent it to?
 - Are you concerned that institutions or secret services could collect and analyze the data that you are disclosing on the Internet?
 - Are you concerned that website providers are tracking your online activities?
 - Are you concerned that you don’t know what other organizations or website providers are doing with you data?

@@

 - Financial information (bank data, account balances…)
 - Medical information (health, medical records…)
 - Second name
 - First name
 - Residence
 - Street and house number
 - Email address
 - Phone number
 - Job (past and present)
 - Education
